%-------------------------
% Resume in Latex
% Author : Arun Jois
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\pdfgentounicode=1
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[ \vspace{-5pt}]
%}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{ #2 \vspace{-2pt}}
	}
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
	\begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\href{http://sourabhbajaj.com/}{\Large Arun S Jois}} & Email : \href{mailto:arunsjois@outlook.com}{arunsjois@outlook.com}\\
		\href{https://github.com/arunjois} {https://github.com/arunjois} & 
		\href{}{1426/2 Sri Ranga Harsha Mahal Road Hassan-573201}\\ 
		\href{}{DOB:01-02-1997} & \href{}{+91 9964294370}
	\end{tabular*}
	
	%\section{\textbf{EXPERIENCE}}
	
	
	%-----------EXPERIENCE-----------------
	\section{\textbf{EXPERIENCE}}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{NewFold Digital}{Bellandur, Bengaluru}
	{Operations Engineer}{Jul 2020 - Aug 2021}
	\resumeItemListStart
	\resumeItem{Linux System Administration\\}
	{Hands on experience in Linux system administration at production level.\\ 
	Exposure to System Engineering.\\
	Experienced in bash scripting/shell 
	scripting.\\ Experienced in troubeleshooting issues related to memory, storage, 
	networking on CentOS.\\  Experience in writing Ansible 
	script for Linux servers.\\ Experience in writing Python script and Perl.\\ } 

	\resumeItem{cPanel-WHM\\}{Troubleshooting customer's cPanel related issues such as 
		assigning quota to accounts(disk space, Email Accounts).\\ 
		Troubleshooting customer's account to move between hosting plan.\\
		Troubleshooting Email related issues in Exim, Dovecot, ApacheSpam Assassin etc. \\
		Troubleshooting issues with WordPress hosted site dealing with PHP and MYSQL. 
		}
	\resumeItem{Provisioning\\}{Exposure in provisioning server with Foreman.\\
			Experience in configuration management using Puppet for Infrastructure as 
			code(IaC).\\ }
	\resumeItem{GitOps\\}{Hands on work experience in GitOps(GitHub \& TravisCI-creating 
		a CI/CD 
		pipeline).\\ 
		Experience in using git to track the configuration and maintain reliability 
		of Infrastructure as code. 
	\\Understands in internal working of Git. }
	\resumeItem{Backups with ZFS\\}
	{ Worked on a project testing the feasibility of ZFS for backup system at scale.\\ 
	Knowledge of internal working of ZFS.
	}
	\resumeItemListEnd
	\resumeSubheading
	{NewFold Digital}{Bellandur, Bengaluru}
	{Intership}{Jan 2020 - May 2020}
	\resumeItemListStart
	\resumeItem{Autoremediation Platform using Stackstorm}
	{A proof of concept for autoremediation platform to diagnose and remediate server 
		without human intervention and also to perform root cause analysis. }
	\resumeItem{Chatbot}{Created a Chatbot service using Google Cloud Pub/Sub and Hubot 
		to run scripts on a target server and also to get system stats such as CPU idle 
		time, RAM usage etc. }
	
	\resumeItemListEnd
	% --------Multiple Positions Heading------------
	%    \resumeSubSubheading
	%     {Software Engineer I}{Oct 2014 - Sep 2016}
	%     \resumeItemListStart
	%        \resumeItem{Apache Beam}
	%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
	%     \resumeItemListEnd
	%    \resumeSubHeadingListEnd
	%-------------------------------------------
	\resumeSubHeadingListEnd
	\section{\textbf{KEY SKILLS}}
	\resumeSubHeadingListStart
	\resumeSubItem{}{Linux, LVM, RAID, Linux Filesystems, ZFS,
		OSI Model and Local Area Networking (LAN), MySQL, RDBMS  
		virtualization using libvirtd, qemu, kvm, rsync, Samba, Bash, Java, JavaFX, Python, 
		Perl, Google Cloud Platform (pending 
		certification), GCP, GKE, IAM, Puppet, Foreman, Ansible, Docker, Kubernetes, Git.}
	\resumeSubHeadingListEnd
	%-----------PROJECTS-----------------
	\section{\textbf{PROJECTS}}
	\resumeSubHeadingListStart
	\resumeSubItem{Personal OTT platform using Samba and ZFS}{Created a personal OTT 
	platform using Samba server for media streaming. Currently containerizing the 
	platform using Docker and Kubernetes. }
	\resumeSubItem{PXE-Boot}{Create a PXE Boot setup for personal use.}
	\resumeSubItem{Configuring softwares to automate routine tasks}{Has Experience in 
	configuration vim and tmux. Writing .vimrc and .tmux.conf respectively. Experience in 
	creating aliases command in .bashrc to run bash scripts and create custom commands.}
	\resumeSubItem{Assembling Computer}{Has experience in bulding CPU from scratch. 
	Exceptional understanding of computer hardware.}
	
	\resumeSubItem{Web based LaTeX solution}
	{A web based Latex document generator written in LAMP, where the user can generate 
	a \LaTeX  document without writing a line of latex code. }
	\resumeSubItem{Hospital Management System on MEAN stack}
	{A Hospital bed management system on MEAN stack. Management tool to handle the 
	availability bed in a hospital.}
	\resumeSubItem{Social Media for College}
	{Social Networking for colleges. A website that facilitates social networking for 
		college activities. Written in LAMP \href{https://github.com/arunjois/test} 
		{https://github.com/arunjois/test}}
	\resumeSubHeadingListEnd
	\section{\textbf{ PAPER PRESENTED}}
	\resumeSubHeadingListStart
	\resumeSubItem{Papers Presented} { 
		\href{https://www.ijrte.org/wp-content/uploads/papers/v9i1/A2725059120.pdf}{``Telemetry Based Anomaly Detection and Correlation in Data Center"  (IJRTE) ISSN: 2277-3878, 
			Volume-9 Issue-1, May 2020}}
	\resumeSubHeadingListEnd
	%-----------EDUCATION-----------------
	\section{\textbf{EDUCATION}}
	\resumeSubHeadingListStart
	\resumeSubheading
	{R.V College of Engineering}{Bangalore, KA}
	{Master of Computer Applications-  CGPA: 7.35}{Sept. 2017 -- Jun. 2020}
	\resumeSubheading
	{Govt. Home Science College}{Hassan, KA}
	{Bachelor of Computer Applications-  Percentage:70.66\% }{Aug. 2014 -- Apr. 2017}
	\resumeSubHeadingListEnd
	%
	%--------PROGRAMMING SKILLS------------
	%\section{Programming Skills}
	%  \resumeSubHeadingListStart
	%    \item{
		%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
		%      \hfill
		%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
		%    }
	%  \resumeSubHeadingListEnd
	
	
	%-------------------------------------------
\end{document}
